Privacy and Security Benefits of Jailbreaking iOS

### 2013-12-13 final_project/paper.tex
aa

\subsection{Installing an outbound connections firewall}
Since iOS doesn't come with a user configurable firewall, it is impossible for the end user to monitor the outbound connections that apps attempt. In the case of privacy leaking applications this is of utmost importance as the user can prevent the leaking of information to third party servers shall they notice any suspicious data transfers (e.g. a game connecting to a server different than Apple's Game Center servers. A solution (Firewall iP 2.0) for outbound connection monitoring and control can be downloaded from the Cydia jailbreak app.
\subsection{Disabling anonymous usage statistics}

>>>>

\subsection{Installing an outbound connections firewall}
Since iOS doesn't come with a user configurable firewall, it is impossible for the end user to monitor the outbound connections that apps attempt. In the case of privacy leaking applications this is of utmost importance as the user can prevent the leaking of information to third party servers shall they notice any suspicious data transfers (e.g. a game connecting to a server different than Apple's Game Center servers) A solution (Firewall iP 2.0) for outbound connection monitoring and control can be downloaded from the Cydia jailbreak app.
\subsection{Disabling anonymous usage statistics}
